Oral anticoagulants

### 2021-01-07 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Setting oac analyses as warfarin proportion of all oac

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(!!datename, bnfchem, regional_unit) %>% 
    summarise(n = sum(!!unit)) %>% 
    mutate(n = n / sum(n)) %>% 
    filter(bnfchem == bnf) %>% 
    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                         str_detect(!!datename, pattern = "-03-") ~ n/31,
                         str_detect(!!datename, pattern = "-04-") ~ n/30,
                         str_detect(!!datename, pattern = "-05-") ~ n/31,
                         str_detect(!!datename, pattern = "-06-") ~ n/30,
                         str_detect(!!datename, pattern = "-07-") ~ n/31,
                         str_detect(!!datename, pattern = "-08-") ~ n/31,
                         str_detect(!!datename, pattern = "-09-") ~ n/30,
                         str_detect(!!datename, pattern = "-10-") ~ n/31,
                         str_detect(!!datename, pattern = "-11-") ~ n/30,
                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

## Read from local file
gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL) %>% 
  filter(year == 2020) # do something better
oac_p <- read_rds("../data/oral_anticoagulants.rds")

## Sort into monthly count data
oac_p_monthly_count <- oac_p %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = n / sum(n)) %>% 
  filter(bnfchem == warf) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>%
    as_tsibble(index = datename)
```

```{r prep-data}

oac_p_monthly_quantity_hb <- 
  right_join(oac_p, select(gp, c(practiceid, hboard)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(region = hboard, datename = datename, unit = Quantity,
               bnf = warf) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, hboard)) %>% 
  group_by(hboard) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_p_monthly_quantity_cluster <- 
  right_join(oac_p, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_p_monthly_quantity_gp <- 
  propRegional(oac_p, PracticeID, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)

@@

@@

```{r, health-board-modelling}
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))

oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r}
system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))

oac_p_hb_fcsts %>%
  write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))

oac_p_gp_cluster_cv_models %>%
  write_rds("../data/oac_p_gp_cluster_cv_models.rds")

@@

```{r}
system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))

oac_p_gp_cluster_fcsts %>%
  write_rds("../data/oac_p_gp_cluster_fcsts.rds")

@@

system.time(oac_p_gp_cv_models <-
  oac_p_monthly_quantity_gp_pre_cv19 %>%
    filter(!regional_unit %in% incomplete_gp) %>%
              regionalCV())

oac_p_gp_cv_models %>%
  write_rds("../data/oac_p_gp_cv_models.rds")

@@

```{r}
regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
{
  if (!is.logical(keep_fits)) {
    stop("`keep_fits` must be of type logical")
  }
  regions <- unique(data$regional_unit)

  cl <- parallel::makeCluster(8)
  plan(cluster, workers = cl)

  fable_fcst <- 
    future_map_dfr(.x = regions, 
                   .f = ~fableModels(filter(data, 
                                            regional_unit == .x)) %>% 
                     forecast(h = h) %>% as_tibble(), 
                   .options = furrr_options(seed = TRUE))

  message("fable fits complete, step 1/4")
  message("fable forecasts complete, step 2/4")

  prophet_fcst <- 
    future_map_dfr(.x = regions, 
                   .f = ~prophetModels(filter(data, 
                                            regional_unit == .x)) %>% 
                     forecast(h = h) %>% as_tibble(), 
                   .options = furrr_options(seed = TRUE))
  message("prophet fits complete, step 3/4")
  message("prophet forecasts complete, step 4/4")

  parallel::stopCluster(cl)
  plan(sequential)
  joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
    dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
      0.1), med = median(n), ub_80 = quantile(n, 0.9), 
      ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
      dist = n, n = NULL)
      return(list(forecasts = joint_fcst))
}

system.time(oac_p_gp_fcsts <-
              oac_p_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts(keep_fits = TRUE))

oac_p_gp_fcsts %>%
  write_rds("../data/oac_p_gp_fcsts_2.rds")

oac_p_gp_cluster_fcsts <- 
  read_rds("../data/oac_p_gp_fcsts_2.rds")
```

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_hb_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

>>>>

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(!!datename, bnfchem, regional_unit) %>% 
    summarise(n = sum(!!unit)) %>% 
    mutate(n = 100 * n / sum(n),
           log_n = log(n)) %>% 
    filter(bnfchem == bnf) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

## Read from local file
gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL) %>% 
  filter(year == 2020) # Do something better. Is npat important for the proportion?

oac_p <- read_rds("../data/oral_anticoagulants.rds")

## Sort into monthly count data
oac_p_monthly_count <- 
  oac_p %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = 100 * n / sum(n), # make it a percentage rather than proportion
         log_n = log(n)) %>% 
  filter(bnfchem == warf) %>% 
  ungroup() %>%
  as_tsibble(index = datename)

oac_p_monthly_quantity_hb <- 
  right_join(oac_p, select(gp, c(practiceid, hboard)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(region = hboard, datename = datename, unit = Quantity,
               bnf = warf)

oac_p_monthly_quantity_cluster <- 
  right_join(oac_p, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(cluster, datename, Quantity, bnf = warf)

oac_p_monthly_quantity_gp <- 
  propRegional(oac_p, PracticeID, datename, Quantity, bnf = warf)

@@

```{r oac-p-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
oac_p_monthly_count %>% 
  select(datename, n) %>% 
  autoplot() +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

@@

```{r, health-board-modelling}
# system.time(oac_p_hb_cv_models <-
#   regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
# 
# oac_p_hb_cv_models %>%
#   write_rds("../data/oac_p_hb_cv_models.rds")

@@

```{r}
# system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
# 
# oac_p_hb_fcsts %>%
#   write_rds("../data/oac_p_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
# system.time(oac_p_gp_cluster_cv_models <-
#   regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
# 
# oac_p_gp_cluster_cv_models %>%
#   write_rds("../data/oac_p_gp_cluster_cv_models.rds")

@@

```{r}
# plan(multisession)
# system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# oac_p_gp_cluster_fcsts %>%
#   write_rds("../data/oac_p_gp_cluster_fcsts.rds")

@@

# system.time(oac_p_gp_cv_models <-
#   oac_p_monthly_quantity_gp_pre_cv19 %>%
#     filter(!regional_unit %in% incomplete_gp) %>%
#               regionalCV())
# 
# oac_p_gp_cv_models %>%
#   write_rds("../data/oac_p_gp_cv_models.rds")

@@

```{r}
# regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
# {
#   if (!is.logical(keep_fits)) {
#     stop("`keep_fits` must be of type logical")
#   }
#   regions <- unique(data$regional_unit)
#   
#   cl <- parallel::makeCluster(8)
#   plan(cluster, workers = cl)
#   
#   fable_fcst <- 
#     future_map_dfr(.x = regions, 
#                    .f = ~fableModels(filter(data, 
#                                             regional_unit == .x)) %>% 
#                      forecast(h = h) %>% as_tibble(), 
#                    .options = furrr_options(seed = TRUE))
#   
#   
#   message("fable fits complete, step 1/4")
#   message("fable forecasts complete, step 2/4")
# 
#   prophet_fcst <- 
#     future_map_dfr(.x = regions, 
#                    .f = ~prophetModels(filter(data, 
#                                             regional_unit == .x)) %>% 
#                      forecast(h = h) %>% as_tibble(), 
#                    .options = furrr_options(seed = TRUE))
#   message("prophet fits complete, step 3/4")
#   message("prophet forecasts complete, step 4/4")
#   
#   parallel::stopCluster(cl)
#   plan(sequential)
#   joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
#     dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
#       0.1), med = median(n), ub_80 = quantile(n, 0.9), 
#       ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
#       dist = n, n = NULL)
#       return(list(forecasts = joint_fcst))
# }

# system.time(oac_p_gp_fcsts <-
#               oac_p_monthly_quantity_gp_pre_cv19 %>%
#               filter(!regional_unit %in% incomplete_gp) %>%
#               regionalJointFcsts())
# 
# oac_p_gp_fcsts %>%
#   write_rds("../data/oac_p_gp_fcsts.rds")

oac_p_gp_fcsts <- 
  read_rds("../data/oac_p_gp_fcsts.rds")
```

* 2020-12-18 2694 secs

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_hb_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r, eval = FALSE}
# lcmm::

```{r}
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = (n - .mean), # Why are the numbers so small?
         regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  mutate(regional_unit = as.numeric(regional_unit)) %>% 
  write_csv(file = "../data/mplus/oac_cluster_discrep.csv", col_names = FALSE)
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```{r}
best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_p_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = 1000000*(n - .mean), # Why are the numbers so small?
         regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  mutate(regional_unit = as.numeric(regional_unit)) %>% 
  na.omit() %>% .[2:5] %>% min()
  write_csv(file = "../data/mplus/oac_gp_discrep.csv", col_names = FALSE)
```

```{r}
source("../r_scripts/functions/mplus_plotting.R")
mplus.view.plots("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
mplus.plot.estimated_means("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
```
